\documentclass{supervision}
\usepackage{course}

\Supervision{2}

\begin{document}
  \begin{questions}
    \question Read this paper:
      \url{http://research.google.com/archive/chubby-osdi06.pdf} and summarise
      the main contributions to the work described in 300 words.

    \question DNS is a good example of a large-scale distributed system.
      \begin{parts}
        \part Find out how DNS works and write a 300 word summary.

        \part Provide an estimate for the number of DNS lookups which occur on
          the Internet in a typical day. How many queries do you think a single
          4-core server could support?

        \part Describe why the architecture of DNS can support the rate of
          lookups you estimated in part (b).

        \part Does DNS support strong or weak consistency? Why? How might you
          demonstrate this one way or another?
      \end{parts}

    \question You have been given a cluster of standard PCs all connected via
      Ethernet and the raw location data from 20 million vehicles in the UK
      for the last full five calendar years. Each location sample of a vehicle
      is stored as four 32-bit values representing:

      \begin{code}{}
        <vehicle id>, <timestamp>, <longitude>, <latitude>
      \end{code}

      A location sample is captured every second the vehicle's engine is
      running. You have been asked to use the Map-Reduce framework to generate
      summary statistics of the data.

      \begin{parts}
        \part Estimate the total number of samples in the data set.

        \part Describe how you would divide up the raw data and distributed it
          across the hard drives in the PCs.

        \part Describe how you would use the Map-Reduce framework to distribute
          the processing required to calculate the following statistics:

          \begin{subparts}
            \subpart The vehicle which drove the most miles
            \subpart The 20 most frequently visited locations in the UK
            \subpart The minimum, average and maximum speed on each 1km stretch
              of UK motorway for each hour of each day in the week
          \end{subparts}

        \part How many PCs will you need in the cluster to calculate the
          statistics in a timely fashion?
      \end{parts}

    \question Describe what role-based access control is. As the managing
      director of a large bank, describe how you could use role-based access
      control to manage the risk posed by corrupt employees.

  \end{questions}
\end{document}
